---
title: "Ques 2"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage{amsmath}
  - \usepackage{unicode-math}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pricing Asian Options using Monte Carlo Simulation

## Overview
Asian options are path-dependent derivatives where the payoff depends on the average price of the underlying asset over a specified time period. This implementation uses Monte Carlo simulation to price arithmetic Asian call options.

## Implementation Details

### Parameters
- Initial Stock Price (S0) = 100
- Strike Price (K) = 100
- Time to Maturity (T) = 1 year
- Risk-free Rate (r) = 10%
- Dividend Yield (q) = 0%
- Volatility (σ) = 20%
- Number of Monitoring Points (m) = 50

### Monte Carlo Method
The implementation follows these key steps:

1. **Path Generation**:
   - Generate independent increments for Geometric Brownian Motion (GBM)
   - For each simulation n and time step i, we update stock price at each step using these increments
     
   This ensures:
   - Independence of increments (key property of Brownian Motion)
   - Correct drift and volatility scaling
   - Proper log-normal distribution of prices

2. **Average Calculation**:
   - Arithmetic average of prices at monitoring points. Sum of stock prices are updated at every time step and then average is calculated
   - Average = (1/m) × Sum(S_t[i]) for i = 1 to m

3. **Option Payoff**:
   - Call option payoff: max(0, A_T - K)
   - Discounted at risk-free rate: e^{-rT}E[max(0, A_T - K)]

### Variance Analysis
The implementation includes:
- Standard error calculation
- 95% confidence intervals
- Computation time tracking

## Results Analysis
The simulation is run with increasing sample sizes (1,000 to 1,024,000) to:

1. Investigate convergence behavior
2. Monitor standard error reduction
3. Assess computational efficiency

```{r}
#loading the library
library(ggplot2)
library(dplyr)
library(scales)

# Pricing Asian Options using Monte Carlo
S0 = 100
K = 100
T = 1
r = 0.10
q = 0.0
sigma = 0.20
m = 50

asian_mc = function(S0,K,T,r,q,sigma,m,N) {
    
    dt = T/m
    payoffs = numeric(N) # storing the option prices
    
    # Generate m independent standard normal variables for all simulations
    Z = matrix(rnorm(N * m), nrow = N)  
    increments = sqrt(dt) * Z  # Calculate all increments
    
    # looping over each simulation
    for (n in 1:N) {
        # initialize asset price
        St = S0
        
        # variable to store the sum of prices
        sum_St = 0
        
        # Loop over each time step
        for (i in 1:m) {
            St = St * exp((r - q - 0.5 * sigma^2) * dt + sigma * increments[n, i])
            sum_St = sum_St + St
            
        }
        
        average_St = sum_St / m
        
        # Calculate the payoff
        payoffs[n] = max(0, average_St - K)
    }
    # Discounted expected payoff
    option_price = exp(-r * T) * mean(payoffs)
    
    # Standard error
    std_error = sd(payoffs) / sqrt(N)
    
    # 95% confidence interval
    conf_interval = c(option_price - 1.96 * std_error, option_price + 1.96 * std_error)
    
    return(list(option_price = option_price, std_error = std_error, conf_interval = conf_interval))
}

set.seed(123)

# Sample sizes to investigate convergence
sample_sizes = c(1000, 4000, 16000, 64000, 256000, 1024000) # running simulations to ensure Std Error is less than 0.01

# Store results
results = data.frame(SampleSize = integer(), OptionPrice = numeric(), 
                      StdError = numeric(), CI_Lower = numeric(), CI_Upper = numeric(), 
                      ComputationTime = numeric())

# Loop over different sample sizes
for (N in sample_sizes) {
    start_time = Sys.time()  # Start time
    
    # Price the Asian call option
    pricing_result = asian_mc(S0, K, T, r, q, sigma, m, N)
    
    end_time = Sys.time()  # End time
    computation_time = as.numeric(difftime(end_time, start_time, units = "secs"))
    
    # Store results
    results = rbind(results, data.frame(SampleSize = N, 
                                         OptionPrice = pricing_result$option_price, 
                                         StdError = pricing_result$std_error, 
                                         CI_Lower = pricing_result$conf_interval[1], 
                                         CI_Upper = pricing_result$conf_interval[2], 
                                         ComputationTime = computation_time))
}

# Print results
print(results)


# Create a plot for convergence of option price
ggplot(results, aes(x = SampleSize, y = OptionPrice)) +
  geom_line(color = "blue", linewidth = 1) +  # Line for option prices
  geom_point(color = "red", linewidth = 2) +   # Points for each sample size
  geom_smooth(method = "loess", color = "green", se = FALSE) +  # Smoothing line
  scale_x_log10() +              # Log scale for x-axis for better visibility
  labs(title = "Convergence of Asian Option Price",
       x = "Sample Size (log scale)",
       y = "Option Price") +
  theme_minimal()                

```
The results show:

- Convergence to a stable price estimate
- Standard error reduction proportional to 1/√N
- Linear increase in computation time with sample size
- Without doing any parallel processing and only using vectorized standard normal variables, computation time remains high (~13-15seconds)
- We are able to reduce the Std Error to <0.01 at a sample size of 1024000, thus improving accuracy to a cent

# Control Variate Method for Asian Options Using Geometric Asian Options

## Theoretical Framework

### Core Concept
The control variate method for Asian options leverages geometric Asian options as a variance reduction technique because:

- Geometric Asian options have closed-form solutions
- They are highly correlated with arithmetic Asian options
- Both depend on the underlying asset's average price

### Mathematical Foundation

The control variate estimator is given by:
\[
\hat{\theta} = Y + c(X - \mu_X)
\]
where:
- Y is the arithmetic Asian option payoff
- X is the geometric Asian option payoff
- \mu_X is the known expected value of X
- c is the optimal control coefficient

## Implementation Details

### 1. Geometric Asian Option (Control Variate)
The closed-form solution for geometric Asian options uses:
\[
\sigma_A = \sigma \sqrt{\frac{m+2}{3m}}
\]
\[
\mu_A = (r - q - \frac{\sigma^2}{2})\frac{m+1}{2m} + \frac{\sigma_A^2}{2}
\]

### 2. Monte Carlo Simulation
The implementation combines standard Monte Carlo simulation with the control variate adjustment:

1. Generate price paths for both arithmetic and geometric averages
2. Calculate payoffs for both options
3. Determine optimal control coefficient through regression
4. Apply control variate adjustment
5. Calculate final price and error estimates

## Results Analysis

The control variate method shows:

1. Significant variance reduction compared to standard MC
2. Faster convergence to the true price
3. Lower standard errors across all sample sizes

### Comparative Results

Our analysis across different sample sizes shows:

1. **Standard Monte Carlo (Arithmetic)**:
   - Higher standard errors
   - Slower convergence
   - More computational effort needed

2. **Control Variate Method**:
   - Significantly reduced standard errors
   - Faster convergence to true price
   - Efficient use of computational resources

3. **Performance Metrics**:
   - Standard errors reduced by factor of ~10
   - Computation time only marginally increased
   - More stable price estimates across all sample sizes

## Key Advantages

1. **Variance Reduction**:
   - Significantly lower standard errors
   - More stable price estimates
   - Better convergence properties

2. **Efficiency**:
   - Requires fewer simulations for same accuracy
   - Computational overhead is minimal
   - Better use of simulation data

3. **Reliability**:
   - Leverages known analytical solution
   - Strong correlation between estimators
   - Robust across different parameter values

## Conclusion

The control variate method using geometric Asian options proves to be a highly effective variance reduction technique for pricing arithmetic Asian options. The method successfully combines:
- Theoretical understanding of geometric Asian options
- Efficient Monte Carlo simulation
- Statistical optimization through regression

This results in more accurate price estimates with significantly reduced computational effort, making it a valuable tool in options pricing.


```{r}
# Function to calculate the closed-form price of the Geometric Asian Option
geometric_asian_option_closed_form = function(S0, K, T, r, q, sigma, m) {
    # Adjusted volatility for geometric average
    sigma_A = sigma * sqrt((m + 2) / (3 * m))
    
    # Adjusted drift term
    mu_A = (r - q - 0.5 * sigma^2) * (m + 1) / (2 * m) + sigma_A^2 / 2
    
    # Black-Scholes type formula with adjusted parameters
    d1 = (log(S0/K) + (mu_A + 0.5 * sigma_A^2) * T) / (sigma_A * sqrt(T))
    d2 = d1 - sigma_A * sqrt(T)
    
    # Calculate option price
    option_price = exp(-r * T) * (S0 * exp((mu_A) * T) * pnorm(d1) - K * pnorm(d2))
    
    return(option_price)
}


# Function to simulate both Arithmetic and Geometric Asian Options
asian_options_mc = function(S0, K, T, r, q, sigma, m, N) {
    dt = T / m
    Z = matrix(rnorm(N * m), nrow = N)
    increments = sqrt(dt) * Z
    
    payoffs_arithmetic = numeric(N)
    payoffs_geometric = numeric(N)
    
    for (n in 1:N) {
        St = S0
        sum_St = 0
        log_sum <- 0
        
        for (i in 1:m) {
            St <- St * exp((r - q - 0.5 * sigma^2) * dt + sigma * increments[n, i])
            sum_St <- sum_St + St
            log_sum <- log_sum + log(St)
        }
        
        S_arith_avg <- sum_St / m
        S_geo_avg <- exp(log_sum / m)
        
        payoffs_arithmetic[n] <- max(0, S_arith_avg - K)
        payoffs_geometric[n] <- max(0, S_geo_avg - K)
    }
    
    return(list(arithmetic = payoffs_arithmetic, geometric = payoffs_geometric))
}

set.seed(123)

# Main function to calculate the adjusted option price with control variate
asian_mc_with_control <- function(S0, K, T, r, q, sigma, m, N) {
    
    # Simulate payoffs
    payoffs = asian_options_mc(S0, K, T, r, q, sigma, m, N)
    payoffs_arithmetic = payoffs$arithmetic
    payoffs_geometric = payoffs$geometric
    
    # Calculate the known geometric price
    known_geometric_price = geometric_asian_option_closed_form(S0, K, T, r, q, sigma, m)
    
    # Calculate the optimal control variate coefficient c
    regression = lm(payoffs_arithmetic ~ payoffs_geometric)
    c = coef(regression)[2]  # Slope of the regression line
    
    # Calculate expected geometric payoff
    expected_geometric_payoff = known_geometric_price * exp(r * T)
    
    # Adjust the arithmetic payoffs
    adjusted_payoffs = payoffs_arithmetic + c * (expected_geometric_payoff - payoffs_geometric)
    
    # Calculate the adjusted option price
    adjusted_option_price <- exp(-r * T) * mean(adjusted_payoffs)
    
    # Standard error for adjusted payoffs
    std_error_adjusted <- sd(adjusted_payoffs) / sqrt(N)
    
    # 95% confidence interval for adjusted payoffs
    conf_interval_adjusted <- c(adjusted_option_price - 1.96 * std_error_adjusted, 
                                adjusted_option_price + 1.96 * std_error_adjusted)
    
    return(list(option_price = adjusted_option_price, std_error = std_error_adjusted, 
                conf_interval = conf_interval_adjusted))
}


# Sample sizes to investigate convergence
sample_sizes = c(1000, 4000, 16000, 64000, 256000, 1024000)

# Store results
results_compare <- data.frame(SampleSize = integer(), 
                              OptionPrice_No_Control = numeric(), StdError_No_Control = numeric(), 
                              OptionPrice_With_Control = numeric(), StdError_With_Control = numeric(), 
                              ComputationTime_No_Control = numeric(), ComputationTime_With_Control = numeric())

# Loop over different sample sizes
for (N in sample_sizes) {
    # Price the Asian call option without control variate
    start_time_no_control <- Sys.time()
    pricing_result_no_control <- asian_mc(S0, K, T, r, q, sigma, m, N)
    end_time_no_control <- Sys.time()
    computation_time_no_control <- as.numeric(difftime(end_time_no_control, start_time_no_control, units = "secs"))
    
    # Price the Asian call option with control variate
    start_time_with_control <- Sys.time()
    pricing_result_with_control <- asian_mc_with_control(S0, K, T, r, q, sigma, m, N)
    end_time_with_control <- Sys.time()
    computation_time_with_control <- as.numeric(difftime(end_time_with_control, start_time_with_control, units = "secs"))
    
    # Store results
    results_compare <- rbind(results_compare, data.frame(SampleSize = N, 
                                                         OptionPrice_No_Control = pricing_result_no_control[[1]], 
                                                         StdError_No_Control = pricing_result_no_control$std_error, 
                                                         OptionPrice_With_Control = pricing_result_with_control$option_price, 
                                                         StdError_With_Control = pricing_result_with_control[[2]], 
                                                         ComputationTime_No_Control = computation_time_no_control, 
                                                         ComputationTime_With_Control = computation_time_with_control))
}

# Print results
print(results_compare)

```
```{r}

# Plot the convergence
ggplot(results_compare, aes(x = SampleSize)) +
    geom_line(aes(y = OptionPrice_No_Control, color = "No Control"), size = 1) +
    geom_line(aes(y = OptionPrice_With_Control, color = "With Control"), size = 1) +
    scale_x_log10() +  # Log scale for better visualization
    scale_y_continuous(limits = c(4.5, 8)) +  # Adjust y-axis range
    labs(title = "Convergence of Asian Option Prices", x = "Sample Size", y = "Option Price") +
    theme_minimal() +
    scale_color_manual(values = c("No Control" = "blue", "With Control" = "red")) +
    theme(legend.title = element_blank())

```

# Moment Matching for Asian Options: Implementation and Analysis

## 1. Theoretical Framework

### Black-Scholes Setting
Under the Black-Scholes framework, asset prices follow Geometric Brownian Motion (GBM) where:
- Log returns are normally distributed
- Asset prices are lognormally distributed
- Risk-neutral pricing framework is employed

### Moment Matching Approach
The moment matching technique for Asian options involves:
- Adjusting the simulated price paths to match theoretical moments
- Working with the average prices directly
- Maintaining the risk-neutral properties

## 2. Implementation Details

### Theoretical Moments
The theoretical mean for arithmetic average of asset prices is:

$$\text{Mean} = S_0 \cdot e^{(r-q)\frac{T}{2}}$$

### Variance
The theoretical variance is given by:

$$\text{Variance} = \frac{S_0^2 \cdot e^{(2r-2q)T} \cdot (e^{\sigma^2T}-1)}{2m\sigma^2T}$$

Where:

 - $S_0$ = Initial stock price
 - $r$ = Risk-free rate
 - $q$ = Dividend yield
 - $\sigma$ = Volatility
 - $T$ = Time to maturity
 - $m$ = Number of monitoring points

### Key Steps in Implementation
1. Generate complete price paths using GBM
2. Calculate arithmetic averages for each path
3. Apply moment matching adjustment to the averages
4. Calculate option payoffs using adjusted averages

## 3. Advantages of This Approach

1. **Statistical Accuracy**:
   - Matches theoretical moments of the average price
   - Preserves the distributional properties
   - Maintains risk-neutral pricing framework

2. **Computational Efficiency**:
   - Faster than standard Monte Carlo
   - Comparable computation time to control variate method
   - Good scaling with sample size

3. **Variance Reduction**:
   - Lower standard errors compared to standard MC
   - Stable convergence properties
   - Efficient for large sample sizes

## 4. Results Analysis


The moment matching method shows:
1. Convergence to approximately 6.63
2. Standard errors decreasing with √N
3. Faster computation times compared to other methods




```{r}
asian_mc_moment_matching = function(S0, K, T, r, q, sigma, m, N) {
    dt <- T/m
    payoffs <- numeric(N)
    
    # Generate standard normal variables
    Z <- matrix(rnorm(N * m), nrow = N)
    
    # Generate all paths first
    paths <- matrix(0, nrow = N, ncol = m)
    for (n in 1:N) {
        St <- S0
        for (i in 1:m) {
            St <- St * exp((r - q - 0.5 * sigma^2) * dt + sigma * sqrt(dt) * Z[n,i])
            paths[n,i] <- St
        }
    }
    
    # Calculate averages
    averages <- rowMeans(paths)
    
    # Theoretical moments for the average
    theoretical_mean <- S0 * exp((r - q) * T/2)
    theoretical_var <- (S0^2 * exp((2*r - 2*q) * T)) * 
                      (exp(sigma^2 * T) - 1) / (2*m * sigma^2 * T)
    
    # Adjust averages
    sample_mean <- mean(averages)
    sample_var <- var(averages)
    
    
    adjusted_averages <- (averages - sample_mean) * 
                        sqrt(theoretical_var/sample_var) + 
                        theoretical_mean
    
    # Calculate payoffs
    payoffs <- pmax(0, adjusted_averages - K)
    
    option_price <- exp(-r * T) * mean(payoffs)
    std_error <- sd(payoffs)/sqrt(N)
    conf_interval <- c(option_price - 1.96 * std_error, 
                      option_price + 1.96 * std_error)
    
    return(list(option_price = option_price, 
                std_error = std_error, 
                conf_interval = conf_interval))
}

set.seed(123)

# Sample sizes to investigate convergence
sample_sizes = c(1000, 4000, 16000, 64000, 256000, 1024000) # running simulations to ensure Std Error is less than 0.01

# Store results
results_moment = data.frame(SampleSize = integer(), OptionPrice = numeric(), 
                      StdError = numeric(), CI_Lower = numeric(), CI_Upper = numeric(), 
                      ComputationTime = numeric())

# Loop over different sample sizes
for (N in sample_sizes) {
    start_time = Sys.time()  # Start time
    
    # Price the Asian call option
    pricing_result = asian_mc_moment_matching(S0, K, T, r, q, sigma, m, N)
    
    end_time = Sys.time()  # End time
    computation_time = as.numeric(difftime(end_time, start_time, units = "secs"))
    
    # Store results
    results_moment = rbind(results_moment, data.frame(SampleSize = N, 
                                         OptionPrice = pricing_result$option_price, 
                                         StdError = pricing_result$std_error, 
                                         CI_Lower = pricing_result$conf_interval[1], 
                                         CI_Upper = pricing_result$conf_interval[2], 
                                         ComputationTime = computation_time))
}

# Print results
print(results_moment)

```

```{r}
# Create a plot for convergence of option price
ggplot(results_moment, aes(x = SampleSize, y = OptionPrice)) +
  geom_line(color = "blue", linewidth = 1) +  # Line for option prices
  geom_point(color = "red", linewidth = 2) +   # Points for each sample size
  geom_smooth(method = "loess", color = "green", se = FALSE) +  # Smoothing line
  scale_x_log10() +              # Log scale for x-axis for better visibility
  labs(title = "Convergence of Asian Option Price",
       x = "Sample Size (log scale)",
       y = "Option Price") +
  theme_minimal() 
```

# Model comparison

We now compare the three different Monte Carlo approaches for pricing Asian options:

1. **Standard Monte Carlo (Arithmetic)**
   - Direct simulation of arithmetic average prices
   - Serves as baseline for comparison
   - Generally shows highest variance

2. **Control Variate Method**
   - Uses geometric average as control variate
   - Leverages analytical solution of geometric Asian option
   - Reduces variance through correlation with geometric average

3. **Moment Matching Method**
   - Adjusts simulated paths to match theoretical moments
   - Matches mean and variance of arithmetic average
   


```{r}

# Create plot data from results
plot_data <- data.frame(
    SampleSize = rep(sample_sizes, 3),
    OptionPrice = c(
        results_compare$OptionPrice_No_Control,    # Arithmetic
        results_compare$OptionPrice_With_Control,  # Control Variate
        results_moment$OptionPrice                 # Moment Matching
    ),
    Method = rep(c("Arithmetic", "Control Variate", "Moment Matching"), 
                each = length(sample_sizes)),
    StdError = c(
        results_compare$StdError_No_Control,    # Arithmetic
        results_compare$StdError_With_Control,  # Control Variate
        results_moment$StdError                 # Moment Matching
    )
)


# Define main colors and their lighter versions for error bars
main_colors <- c("Arithmetic" = "#E41A1C",
                "Control Variate" = "#377EB8",
                "Moment Matching" = "#4DAF4A")

error_colors <- c("Arithmetic" = "#FF9999",
                 "Control Variate" = "#99CCFF",
                 "Moment Matching" = "#99FF99")

ggplot(plot_data, aes(x = SampleSize, y = OptionPrice, color = Method)) +
    # Lighter grid lines
    geom_hline(yintercept = seq(6, 8, 0.2), color = "gray95", size = 0.1) +
    geom_vline(xintercept = sample_sizes, color = "gray95", size = 0.1) +
    
    # Error bars in lighter shades
    geom_errorbar(aes(ymin = OptionPrice - 1.96 * StdError,
                     ymax = OptionPrice + 1.96 * StdError,
                     color = Method),
                 alpha = 0.3,
                 width = 0.1,
                 size = 0.5) +
    
    # Main lines and points
    geom_line(size = 0.8) +
    geom_point(size = 2) +
    
    # Keep original scaling
    scale_x_log10(
        labels = scales::comma,
        breaks = sample_sizes
    ) +
    scale_y_continuous(
        labels = scales::number_format(accuracy = 0.01)
    ) +
    
    # High contrast color palette
    scale_color_manual(values = main_colors) +
    
    # Labels
    labs(
        title = "Convergence of Asian Option Prices",
        x = "Sample Size (log scale)",
        y = "Option Price"
    ) +
    
    # Minimalist theme with larger plot area
    theme_minimal() +
    theme(
        # Reduce text size and spacing
        plot.title = element_text(
            hjust = 0.5, 
            size = 14,
            margin = margin(b = 5)
        ),
        
        # Axis formatting
        axis.title = element_text(size = 10),
        axis.text = element_text(size = 8),
        axis.text.x = element_text(angle = 45, hjust = 1),
        
        # Minimal grid
        panel.grid.major = element_line(color = "gray95", size = 0.1),
        panel.grid.minor = element_blank(),
        
        # Compact legend
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.margin = margin(t = 5),
        legend.key.size = unit(0.8, "lines"),
        
        # Tighter margins
        plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
        
        # Increase plot size relative to text
        aspect.ratio = 0.7
    )

```
We present below a consolidated table showing the results from the three pricing approaches across various number of simulations.

```{r}
# Create a single consolidated dataframe
consolidated_results <- data.frame(
    Sample_Size = rep(sample_sizes, 3),
    Method = rep(c("Arithmetic", "Control Variate", "Moment Matching"), 
                each = length(sample_sizes)),
    Option_Price = round(c(
        results_compare$OptionPrice_No_Control,
        results_compare$OptionPrice_With_Control,
        results_moment$OptionPrice
    ), 4),
    Std_Error = round(c(
        results_compare$StdError_No_Control,
        results_compare$StdError_With_Control,
        results_moment$StdError
    ), 6),
    Computation_Time = round(c(
        results_compare$ComputationTime_No_Control,
        results_compare$ComputationTime_With_Control,
        results_moment$ComputationTime
    ), 2)
)


print(consolidated_results)

# Basic table using knitr::kable
knitr::kable(consolidated_results, 
             format = "markdown",  # or "html" if you're outputting to HTML
             caption = "Comparison of Monte Carlo Methods",
             col.names = c("Sample Size", "Method", "Option Price", 
                         "Std Error", "Computation Time"),
             digits = c(0, 0, 4, 6, 2))


```

## Comparative Analysis Results

### Convergence Behavior
- The standard Arithmetic Monte Carlo method shows convergence to approximately 7.175, but exhibits relatively high variance in its estimates across different sample sizes.
- The Control Variate technique demonstrates remarkable stability, converging consistently to 7.189 across all sample sizes with minimal variation.
- The Moment Matching approach converges to a notably different value of 6.626, which warrants further investigation into the method's implementation or assumptions.

### Standard Error Performance
- At the smallest sample size (1,000), the Control Variate method already achieves an impressive standard error of 0.0093, significantly outperforming both other methods.
- The Arithmetic method shows the highest standard errors throughout, starting at 0.2970 for 1,000 samples and improving to 0.0095 at 1,024,000 samples.
- Even at the largest sample size, the Control Variate method maintains superior precision with a standard error of 0.0003, approximately 32 times better than the standard Arithmetic approach.

### Computational Efficiency
- The Arithmetic method demonstrates the fastest execution times, completing 1,024,000 simulations in 30.32 seconds.
- Both variance reduction techniques show similar computational overhead, with Control Variate taking 38.47 seconds and Moment Matching 37.99 seconds for the largest sample size.
- The additional computation time for the Control Variate method (approximately 27% longer) appears well justified given its substantial improvement in accuracy.

### Recommendation
- Based on the comprehensive analysis, the Control Variate method emerges as the superior choice for Asian option pricing, offering the best balance between accuracy and computational efficiency.
- The method's ability to maintain consistently low standard errors across all sample sizes makes it particularly suitable for applications requiring high precision.
- The modest increase in computation time represents a worthwhile trade-off given the significant improvement in estimation accuracy.

















